Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex
commas
meh

\documentclass{article}
\usepackage{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{multirow}
\title{Word Sense Disambiguation\\
\small{Leveraging the NLTK Toolkit and External Tools}}
\author{
Alec Story
Ansu Abraham
Craig Frey\\
Dustin Tiedemann
Michael Zhu
Thomas Levine
Whitney Foster\\
}

@@

%\begin{figure}[h]
%\includegraphics[width=\textwidth]{pg_0001}
%\caption{\label{fig1}}
%\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{pg_0003}
\caption{\label{fig3}}
\end{figure}

@@

Our run with the highest overall F-measure (overall precision 0.718, overall
recall 0.610), used co-occurrence, collocation out to a distance of 2, base word,
no dependency parsing, and bootstrapped once:

>>>>

\documentclass{article}
\usepackage{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{multirow}
\title{Word Sense Disambiguation\\
\small{Leveraging the NLTK Toolkit and External Tools}}
\author{
Alec Story,
Ansu Abraham,
Craig Frey,\\
Dustin Tiedemann,
Michael Zhu,
Thomas Levine,
Whitney Foster\\
}

@@

@@

\begin{figure}
\includegraphics[width=\textwidth]{pg_0003}
\caption{\label{fig3}Performance for systems with collocation window of size between 2 and 4}
\end{figure}

@@

Our run with the highest overall F-measure (overall precision 0.718, overall
recall 0.610), used co-occurrence, collocation out to a distance of 2, base word,
no dependency parsing, and bootstrapped once:
\newpage
